Quality Assessment of OpenStreetMap Footpath Data

### 2020-08-25 report/report.tex
Remove SLU abbreviation from abstract

As a secondary study, the positional accuracy of the OSM dataset was calculated, since the positional accuracy determines the maximum tolerance in distance between points before it is certain that a road overlaps with another road or building.
Any geographic dataset has a limit on its positional accuracy, which is determined by the theoretical precision of the measuring methods.
In this project, the accuracy was obtained by comparing coordinate points of OSM building footprints to those in the Swedish University of Agricultural Sciences (SLU) building dataset, whose accuracy is known.
\end{abstract}

@@

Som en andra del av studien har felmarginalen för OSM-datamängden också tagits fram, eftersom felmarginalen bestämmer toleransen mellan två punkter som kan tillåtas innan man är säker på att en väg börjar överlappa med en annan väg eller en byggnad.
Varje geografisk datamängd har en gräns på hur väl den stämmer överrens med verkligheten, som bestäms av vilka mätmetoder som har använts i datans insamling.
I detta projekt uppskattades felmarginalen genom att jämföra byggnaders koordinatpunkter i datamängen med de från en referenskarta från Svenska Lantbruksuniversitetet (SLU) med känd felmarginal.
\end{abstract}
\end{otherlanguage}

>>>>

As a secondary study, the positional accuracy of the OSM dataset was calculated, since the positional accuracy determines the maximum tolerance in distance between points before it is certain that a road overlaps with another road or building.
Any geographic dataset has a limit on its positional accuracy, which is determined by the theoretical precision of the measuring methods.
In this project, the accuracy was obtained by comparing coordinate points of OSM building footprints to those in the Swedish University of Agricultural Sciences building dataset, whose accuracy is known.
\end{abstract}

@@

Som en andra del av studien har felmarginalen för OSM-datamängden också tagits fram, eftersom felmarginalen bestämmer toleransen mellan två punkter som kan tillåtas innan man är säker på att en väg börjar överlappa med en annan väg eller en byggnad.
Varje geografisk datamängd har en gräns på hur väl den stämmer överrens med verkligheten, som bestäms av vilka mätmetoder som har använts i datans insamling.
I detta projekt uppskattades felmarginalen genom att jämföra byggnaders koordinatpunkter i datamängen med de från en referenskarta från Svenska Lantbruksuniversitetet med känd felmarginal.
\end{abstract}
\end{otherlanguage}
